%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}


%---------------------------------------------------------
  \cventrynew
    {Brainchip, \textnormal{\textit{Robotics \& AI Solutions Architect Intern} | Remote}} % Job title
    {May 2023 - Aug 2023} % Date (s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and deployed {\bf RL} models for robotic systems, integrating {\bf physics engines} to solve real-world problems.}
        \item {Drove advanced solutions, optimizing robotic platform performance and stability through {\bf ML-driven control systems}.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventrynew
    {NICE Lab -- Stretch RE1, \textnormal{\textit{Research Volunteer} (Prof. Zhe Xu) | Arizona, USA}} % Organisation
    % {} % Job title % Job title
    % {TamilNadu, India} % Location
    {Jan 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop and evaluate differential control synthesis algorithms for multi-agent systems.} 
        \item {Conduct perception and RL research with the Hello Robot, focusing on causal inference and counterfactuals for RL.}
      \end{cvitems}
      }


%---------------------------------------------------------
  \cventrynew
    % {} % Organisation
    {Indian Institute of Technology Bombay, \textnormal{\textit{Robotic Software Engineer Intern} | Remote}} % Job title
    % % {Bombay, India} % Location
    {May 2020 - July 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led an 8-person team to develop a {\bf fiducial-marker-based localization} model for an unstable camera feed.}
        \item {Optimized the localization model using {\bf V-rep} for real-time camera feeds, achieving a calibration error of \leq  0.5\%.}
        \item {Designed a rule-based visual scripting framework for configuring {\bf auto-evaluators} through {\bf B0RemoteAPI} for evaluation.}
        \item {Incorporated a {\bf unit testing} framework with automated test cases to validate the auto-evaluator model.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    { e-Yantra -- Quadraped Bot, \textnormal{\textit{Co-Founder and Team Lead -- Robotic Engineer} | Bihar, India}} % Organisation
    % {} % Job title % Job title
    % {TamilNadu, India} % Location
    {Aug 2019 - Feb 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a 4 member team of IIT Patna’s student quadruped robot team to National (India) Finalist Status (99.7 percentile).} 
        \item {Built a robot from scratch possessing vision, picking, placing, and autonomous decision-making capabilities.}
        \item {Worked with {\bf 2D Path Planning}(A* \& Dijkstra) algorithms to take the shortest path during natural emergencies.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventrynew
    {Neyveli Lignite Corporation India Ltd. (NLCIL) : \textnormal{\textit{Mechanical Engineer Intern} | Neyveli, India}} % Organisation
    % {} % Job title % Job title
    % {TamilNadu, India} % Location
    {June 2019 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved circulating water pump efficiency by 8.44\% using {\bf coating technologies} with a payback period of < 2 months.} 
        \item {Led team to assess and maintain water circulating pump through coatings, showcasing strong team leadership skills.}
      \end{cvitems}
      }

%---------------------------------------------------------
\end{cventries2}
